Medical Concept Extraction

### 2012-12-16 paper/paper.tex
Positioning the table better.
Updating data set section.

The data set that we used train and test the system came from the i2b2 NLP challenge. As mentioned before, the data was already divided into test and training sets and every word was pre-labeled with the following classes: ``problem'', ``test'', ``treatment'', or ``none''.

The training data consisted of 170 medical records and the test data consisted of 256 medical records.  The overall size of the data was 10mb. The data all came from Boston-area hospitals and is subject to a data usage agreement.

@@

\begin{figure}
\begin{center}
	\begin{tabular}{|l|l|l|l|}
	\hline
	\multicolumn{4}{|c|}{\bf crfsuite} \\ \hline
	{\bf Label} & {\bf Precision} & {\bf Recall} & {\bf F1} \\ \hline

>>>>

Deidentified clinical records used in this research were provided by the i2b2 National Center for Biomedical Computing funded by U54LM008748 and were originally prepared for the Shared Tasks for Challenges in NLP for Clinical Data organized by Dr. Ozlem Uzuner, i2b2 and SUNY. As mentioned before, the data came divided into training and test sets and every word was pre-labeled with the following classes: ``problem'', ``test'', ``treatment'', or ``none''.

The overall size of the data was 10mb and came from Boston-area hospitals and is subject to data use agreements. The training data consisted of 170 medical records and the test data consisted of 256 medical records. Further, the distribution over labels of the training and test sets is provided in:

@@

\begin{figure}[t]
\begin{center}
	\begin{tabular}{|l|l|l|l|}
	\hline
	\multicolumn{4}{|c|}{\bf crfsuite} \\ \hline
	{\bf Label} & {\bf Precision} & {\bf Recall} & {\bf F1} \\ \hline
